---
title: "PhD Presentation"
author: Jean-Baptiste Laurent
date: July 27, 2020
output:
    beamer_presentation:
        latex_engine: xelatex
        theme: "CambridgeUS"
        colortheme: "seahorse"
        fonttheme: "structurebold"
---

<!-- Init of R -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(results = 'hide')
# some comment
```

<!-- TOC -->
```{r engine="bash", comment=">"}
grep -E "^# [A-Z]" < presentation.Rmd
```

---

# Self and PhD group presentation

Me,
Consultant at Faurecia since early January in the RAPIDE team, with a background in cyber security and code automatic analysis
(todo: explain what RAPIDE is, and what it does, and the manager name)

* LAURENT Jean-Baptiste
* MENSUEZ Bruno
* RICHELIEU Julien

# Audience

CEO, Directors  managers

# Introduction

Duration of the presentation (30min, 1h ?)
Current model, issues, other areas being worked on.

# Plan of the presentation

# Recap of the market state and opportunities

Shift in the shares with the new model

# Current model vs new model

---

## Current model

---

## Pros, and growing flaws for that model

---

## The new model

---

# The downstream and upstream approach

# Virtualization technologies

Xen, KVM, LXC, QEMU, kqemu (virtualbox / vmware)
[Wikipedia link](https://en.wikipedia.org/wiki/Comparison_of_platform_virtualization_software)

# Expected 3 years road-map

01/07/2020 -> Start of the PhD

01/07/2023 -> End of the PhD

To do on the way:
* Bibliography
* Virtualization tool selection (Tech watch)
* First design

End result: ??

# PhD legal format

# Expected team interactions

# Questions (+ what to remember and abstract)

# Draft notes

Work conditions ?
Current model
New model
Virtualization

Downstream & upstream ?
New technologies ?
Wording ? (skeleton)

Julien expectancy: presenting more in depth the project at its state, so the audience is on point (teams, funds, results who could benefits them).
That would be CTO of Faurecia, Innovative chief, and technical leader, marketing director, Directory R&D soft, Product line and a Manager (do discuss on integrating the software stuff being made).

TODO: need to have a draft for Thursday
