---
title: "Automotive embedded system redesign: addressing the flaws of the current model by creating a new one based on virtualization [^1]"
column_numbers: 3

date: July 27, 2020

primary_colour: "#008080"
secondary_colour: "#0b4545"
accent_colour: "#cc00cc"

titlebox_borderwidth: "1cm"
titlebox_bordercol: "#0b4545"

sectitle_bgcol: "#4b9595"
sectitle_bordercol: "#0b4545"
sectitle_boxshape: "4mm 2mm"

poster_height: "22in"
poster_width: "36in"

logoleft_name: "faurecia_logo.jpeg"
logoright_name: "lrtechnologies_logo.png"

output:
    posterdown::posterdown_html:
        self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

Current **automotive embedded systems** are falling behind due to the **rapidly evolving** automotive market. They become monolithic, costly, and growing further in complexity the longer time goes on.

A **new project** will get presented for a **redesign** of the model based on **virtualization** technologies.

# Involved parties


### **LAURENT Jean-Baptiste**
  + LR-Technology consultant, working for Faurecia
  + Doctoral student

### **RICHEFEU Julien**
  + Faurecia Clarion Electonics, Platform Software Manager
  + PhD Director

### **MENSUEZ Bruno**
  + ENSTA Paris-Tech, Teacher
  + PhD Co-Director

# Models showcase

Design models are standing for the combination of the critical and alternative embedded systems added on top of the physical components like the chassis, the wheels or the engine.

The model is responsible for putting every modern feature together from safety to the passengers comfort. It serves as a reference skeleton and a solid foundation to build upon. 

## **Current model**

Pros|Cons
-|-
Simple model|Difficult to adapt
Straightforward integration|Monolithic architecture
-|Manual subsystem interactions
-|Exponential complexity

## **Concept model**

Pros|Cons
-|-
Modular|Careful design required
Hardware agnostic|Higher entry cost
Re-usable and extensible|
Open to aggressive optimizations|

# Virtualization

* Well documented
* Modular by design
* Secure despite open systems
* Mature technology, limited risks

# Market impact

* Application friendly design
* High customization potential
* Share shift from OEM's to car manufacturers

# Project timeline

* Total of 3 years, research project
  + **Bibliography** and publications: 12-18 months 
  + Project **proposal** and collaboration: 3 months
  + Prototyping work and **project results**: 12-18 months

    
```{r, out.width="100%"}
include_graphics("umls/plantuml_timeline.svg")
```

[^1]: Poster published the 07/07/2020
